\documentclass[12pt]{article}
\usepackage{latexsym, amssymb, amsmath, amsfonts, amscd, amsthm}
\usepackage{enumerate}
\usepackage[margin=1in]{geometry}
\usepackage{calrsfs}
\DeclareMathAlphabet{\pazocal}{OMS}{zplm}{m}{n}
\newcommand{\La}{\mathcal{L}}
\newcommand{\Lb}{\pazocal{L}}
\linespread{1} %Change the line spacing only if instructed to do so.

\newenvironment{problem}[2][Problem]
{
	\begin{trivlist} 
		\item[\hskip \labelsep {\bfseries #1 #2:}]
	}
{
	\end{trivlist}
	}

\newenvironment{solution}[1][Solution]
{
	\begin{trivlist} 
		\item[\hskip \labelsep {\itshape #1:}]
	}
	{
	\end{trivlist}
}

\title{Munkres Chapter 2.17 exercises}
\author{Cherie Li}
\date{06/05/2018}
\begin{document}
\maketitle
\newpage
\begin{problem}[Exercise]{2.17.4}
Show that if $U$ is open in $X$ and $A$ is closed in $X$, then $U-A$ is open in $X$, and $A-U$ is closed in $X$. 
\end{problem}
\begin{solution}
Let $X$ be a set and let $U$ open in $X$ and $A$ closed in. $X$. Notice that $A-U = A \cap U^c$ and that $U-A = U \cap A^c$. By definition of open, $U^c$ is closed. Similarly, by definition of closed, $A^c$ is open. Since the intersection of open sets is also open, $U - A$ closed and since the intersection of closed sets is also closed, $A-U$ closed. 
\end{solution}
\begin{problem}[Exercise]{2.17.11}
Show that the product of two Hausdorff spaces is Hausdorff.
\end{problem}
\begin{solution}
Let $T_1$ and $T_2$ be Haursdorff spaces and let $T_1 \times T_2$ be the product topology. Let $(x_1,y_1) \in T_1 \times T_2$ be arbitrary. Similarly, let 
$(x_2, y_2) \in T_1 \times T_2$ be arbitrary, where $x_1 \neq x_2$ and 
$y_1 \neq y_2$. Then there exist open neighborhoods $U_1, U_2 \in T_1$ and $V_1, V_2 \in T_2$ such that $U_1 \cap U_2 = \varnothing$ 
and $V_1 \cap V_2 = \varnothing$. Then $U_1 \times V_1 \in T_1 \times T_2$ and $U_2 \times V_2 \in T_1 \times T_2$ and are disjoint. By definition, $T_1 \times T_2$ is Hausdorff. 
\end{solution}
\begin{problem}[Exercise]{2.17.12}
Show that a subspace of a Hausdorff space is Hausdorff. 
\end{problem}
\begin{solution}
Let X be a set with topology $T$. Let subspace topology $T_y = \lbrace{Y \cap U| U \in T \rbrace}$. Let $x_1, x_2 \in T_y$ be arbitrary. Then, there exists disjoint open sets $U_1, U_2$ such that $x_1 \in Y \cap U_1$ and $x_2 \in Y \cap U_2$. Then $Y \cap U_1$ and $Y \cap U_2$ also disjoint. Therefore, since $x_1, x_2$ were arbitrary, the subspace is Hausdorff. 
\end{solution}
\begin{problem}[Exercise]{2.17.13}
Show that $X$ is Hausdorff if and only if the diagonal $\triangle = \lbrace{x \times x | x \in X \rbrace}$ is closed in $X \times X$. 
\end{problem}
\begin{solution}
First let $X$ be a Hausdorff space. We want to show $\triangle$ is closed in $X \times X$, which is the same thing as showing the complement is open. Let $\triangle^C = \lbrace{x \times y | x,y \in X, x \neq y\rbrace}$. Since $x \neq y$ and $X$ is Hausdorff, then there exist disjoint open sets $U_1, U_2$ in $X$ such that $x \in U_1$, $y \in U_2$. By definition of product topology, $U_1 \times U_2$ open in $X \times X$. Also, $U_1 \times U_2 \in \triangle ^C$ since they are disjoint. That is, for all $a \times b \in U_1 \times U_2$, $a \in U_1, b \in U_2$ so $a \neq b$. Then by definition of open set, where every point has an open interval containing it contained in the set, $\triangle^C$ is open in $X \times X$. 
\end{solution}
\end{document}


